Cartograms with Dynamic Features

### 2022-03-04 paper/section/main.tex
draft: update figures and algorithms

{
\begin{figure}[b!]
    \centering
    \includegraphics[width=\columnwidth]{example-image-a}
    \caption{An overview of \software. Figure TBA.}
    \label{fig:overview}
\end{figure}
}

{
\begin{figure}[b!]
    \centering
    \includegraphics[width=\columnwidth]{figure/flowchart.png}
    \caption{A flowchart showing the abstraction of our layout algorithm.}
    \label{fig:flowchart}
\end{figure}
}

@@

    \textbf{Local variables:} \\
    $ \nodeListVPSC \gets $ a list of nodes representing CCGs after VPSC \\
    $ \crossRiver \gets $ boolean indicating a node crossed a river \\
    $ \nodeListEach \gets $ a node in $ \nodeList $ \\
    $ \nodeListEachPrevious \gets $ the previous position of $ \nodeListEach $\\
    $ \nodeListVPSCEach \gets $ a node in $ \nodeListVPSC $, which is the next position of $ \nodeListEach $ after VPSC \\

@@

            \State $ \nodeListVPSC \gets $ RunVPSC ($ \nodeList $)

@@

                \If {\Call{TranslateNode}{$ \nodeListEach, \nodeListVPSCEach $}}
                    \State $ \crossRiver \gets $ \Call{TestRiverIntersection}{$ \nodeListEach, \nodeListVPSCEach $}

                    \If{$ \crossRiver = True $}
                        \State $ \nodeListEachStalemate \gets \nodeListEachStalemate + 1 $

                        \If{$ \nodeListEachStalemate < \stalemateMax $}
                            \State $ \nodeListEach(x,y) \gets \nodeListEachPrevious(x,y) $
                        \Else
                            \State \Call{ProcessStalemate}{$ \nodeListEach, \nodeListVPSCEach $}
                            \State $ \nodeListEachStalemate \gets 0 $
                        \EndIf

@@

\begin{algorithm}[tb!]
    \caption{Procedure to update a single node, $ \node $'s position.}\label{alg:move position}

    \textbf{Input:} \\
    $ \node \gets $ the node \\
    $ \nodeVPSC \gets $ the node after running VPSC \\

    \textbf{Output:} \\
    Returns $ True $ if the node's position is updated. \\

    \begin{algorithmic}[1]
        \Procedure{TranslateNode}{$ \node, \nodeVPSC $}
        \If{$ \node(x,y) = \nodeVPSC(x,y) $}
            \item[] \Comment{Node position remains unchanged}
            \State \Return{$ False $}
        \EndIf

        \State $ \node(x,y) \gets \nodeVPSC(x,y) $

        \State \Return{$ True $}
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

@@

% \begin{noindent}
\begin{algorithm}[tb!]
    \caption{Procedure to test if a node, $ \node $ crosses a river.}\label{alg:check river intersection}
    \textbf{Input:} \\
    $ \node \gets $ the node \\
    $ \nodeVPSC \gets $ the node after running VPSC \\

@@

    \begin{algorithmic}[1]
        \Procedure{TestRiverIntersection}{$ \node, \nodeVPSC $}

@@

            \If{$ \nodeBoundingBox ~intersect~ \riverEdgeBoundingBoxEach = True $}
                \If{$ \nodeLineNV ~intersect~ \riverEdgeListEachLine = True $}
                    \State \Return{$ True $}
                \EndIf

                \EndIf
        \EndFor

@@

As the VPSC always tries to produce an optimal node layout where node distribution and translation are minimized, a node might be repeatedly translated between two positions due to river intersection and congestion, creating a stalemate situation, as shown in \figref{fig:stalemate}. In order to create space for VPSC to generate a new layout, we introduce a parameter, $ \stalemateMax $, to test for stalemate. If a node is translated between two positions for more than $ \stalemateMax $ iterations, it is considered to be in a stalemate. A stalemate triggers a corridor derivation, {a corridor is a rectangle with a width of $ \CorridorWidth $ and a length of $ \CorridorLength $, in the direction of the node $ \node $'s previous and current position, denoted $ \nodeVectorPC $ }, all enclosed nodes are then translated in the same direction and by the distance of that vector to alleviate the congestion.

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/stalemate.png}
    \caption{A stalemate situation is when a node repeatedly translates between two positions (A and B) for more than $ stalemate $ iterations. }
    \label{fig:stalemate}
\end{figure}
}

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/corridor.png}
    \caption{When a stalemate occurs, a corridor (black rectangular) is derived based on the current (A) and previous (B) positions of the node that crossed a river, as described in \algoref{alg:derive corridor}. All nodes within the corridor are moved by $ d $ units in the direction of $ \Vector{B}{A} $, e.g, A is moved to C. }
    \label{fig:corridor}
\end{figure}
}

@@

    \textbf{Global variables:} \\
    $ \nodeSize \gets $ the current size of all nodes \\
    $ \CorridorLength \gets $ the length of a corridor \\
    $ \CorridorWidth \gets $ the width of a corridor \\

@@

    \begin{algorithmic}[1]
        \Procedure{ProcessStalemate}{$ \node $}
            \State TranslateNode ($ \node $)

@@

                % TODO: calculate the vector once and use it for all nodes
            \ForEach{$ \nodeInCorridorEach $ inside $ corridor $}
                \State $ \nodeInCorridorEachDx \gets \nodeInCorridorEach.x - \nodeInCorridorEach.previous.x $

                \State $ \nodeInCorridorEachDy \gets \nodeInCorridorEach.y - \nodeInCorridorEach.previous.y $

                \State $ hyp \gets \sqrt{(\nodeInCorridorEachDx)^2 +(\nodeInCorridorEachDy)^2} $

                \State $ \nodeInCorridorEach.next \gets $ \Call{DerivePoint}{$ \Vector{\nodeInCorridorEach.previous}{~\nodeInCorridorEach} $, $ hyp + s $}

                \State TranslateNode ($ \nodeInCorridorEach $, $ \nodeInCorridorEach.next $)

@@

    \textbf{Input:} \\
    $ \Edge \gets $ the edge used to derive the parallel edge $ \EdgeParallel $ \\
    $ \Distance \gets $ the distance between $ \Edge $ and $ \EdgeParallel $ \\

>>>>

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{example-image-a}
    \caption{An overview of \software. Figure TBA.}
    \label{fig:overview}
\end{figure}
}

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/flowchart.png}
    \caption{A flowchart showing the abstraction of our layout algorithm.}
    \label{fig:flowchart}
\end{figure}
}

@@

    \textbf{Local variables:} \\
    $ \nodeListVPSC \gets $ a list of nodes representing CCGs after VPSC \\
    $ \solved \gets True $ if no node crossed a river \\
    $ \crossRiver \gets $ boolean indicating a node crossed a river \\
    $ \nodeListEach \gets $ a node in $ \nodeList $ \\
    $ \nodeListEachPrevious \gets $ the previous position of $ \nodeListEach $\\
    $ \nodeListVPSCEach \gets $ a node in $ \nodeListVPSC $, which is the position of $ \nodeListEach $ after VPSC \\

@@

            \While{$ \solved = False $}

                \State $ \solved \gets True $
                \State $ \nodeListVPSC \gets $ RunVPSC ($ \nodeList $)

@@

                    \If {$ \nodeListEach(x,y) \neq \nodeListVPSCEach(x,y) $}

                        \State $ \crossRiver \gets $ \Call{TestRiverIntersection}{$ \nodeListVPSCEachLine $}
                        \State $ \nodeListEach(x,y) \gets \nodeListVPSCEach(x,y) $

                        \If{$ \crossRiver = True $}

                            \State $ \solved \gets False $
                            \State $ \nodeListEachStalemate \gets \nodeListEachStalemate + 1 $

                            \If{$ \nodeListEachStalemate < \stalemateMax $}

                                \State $ \nodeListEach(x,y) \gets \nodeListEachPrevious(x,y) $

                            \Else

                                \State \Call{ProcessStalemate}{$ \nodeListEach, \nodeListVPSCEach $}
                                \State $ \nodeListEachStalemate \gets 0 $

@@

% \begin{algorithm}[tb!]
%     \caption{Procedure to update the position of a single node $ \node $.}\label{alg:move position}

%     \textbf{Input:} \\
%     $ \node \gets $ the node \\
%     $ \nodeVPSC \gets $ the node after running VPSC \\

%     \textbf{Output:} \\
%     Returns $ True $ if the node's position is updated. \\

%     \begin{algorithmic}[1]
%         \Procedure{TranslateNode}{$ \node, \nodeVPSC $}
%         \If{$ \node(x,y) = \nodeVPSC(x,y) $}
%             \item[] \Comment{Node position remains unchanged}
%             \State \Return{$ False $}
%         \EndIf

%         \State $ \node(x,y) \gets \nodeVPSC(x,y) $

%         \State \Return{$ True $}
%         \EndProcedure
%     \end{algorithmic}
% \end{algorithm}

@@

% \begin{noindent}
\begin{algorithm}[tb!]
    \caption{Procedure to test if a node's translation path, $ \nodeLineNV $ intersects a river.}\label{alg:check river intersection}
    \textbf{Input:} \\
    $ \nodeLineNV \gets $ the node's translation path \\

@@

    \begin{algorithmic}[1]
        \Procedure{TestRiverIntersection}{$ \nodeLineNV $}

@@

            \If{$ \nodeBoundingBox ~intersect~ \riverEdgeBoundingBoxEach = True $}
                \State \Return{$ \nodeLineNV ~intersect~ \riverEdgeListEachLine $}
                \EndIf
        \EndFor

@@

As the VPSC always tries to produce an optimal node layout where node distribution and translation are minimized, a node's translation path might be repeatedly intersecting a river due to congestion, creating a stalemate situation, as shown in \figref{fig:stalemate}. If a node is translated between two positions for $ \stalemateMax $ iterations, a corridor is derived to improve the congestion. \new{A corridor is a rectangle with a width of $ \CorridorWidth $ and a length of $ \CorridorLength $, formed by deriving two edges $ \EdgeParallelA $ and $ \EdgeParallelB $ so that $ \EdgeParallelA \parallel \EdgeParallelA \parallel \nodeLineNpP $ (\figref{fig:corridor}C and D) .} All enclosed nodes are then translated based on $ \nodeVectorPC $ to alleviate the congestion (\figref{fig:corridor}D).

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/stalemate.png}
    \caption{A stalemate situation is when a node's translation path $ \nodeVectorCP $ intersects a river for $ \stalemateMax $ times. A stalemate often occurs when the area is congested and the node is unable to move to a position that is not intersecting a river.}
    \label{fig:stalemate}
\end{figure}
}

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/corridor.png}
    \caption{A stalemate occurs when a node's translation path $ \nodeVectorCP $ intersects a river for $ \stalemateMax $ times, as shown in A. To address the issue, we derive a corridor (orange rectangle in D) based on $ \node $ and $ \nodePrevious $. All nodes within the corridor are translated based on $ \nodeVectorPC $, such that $ \nodeVectorPC = \nodeVectorNNn = \nodeVectorNinNinn $. In order to show a clear illustration, we place nodes sparsely in this figure.}
    \label{fig:corridor}
\end{figure}
}

@@

    \textbf{Global variables:} \\
    $ \CorridorLength \gets $ the length of a corridor \\
    $ \CorridorWidth \gets $ the width of a corridor \\

@@

    \begin{algorithmic}[1]
        \Procedure{ProcessStalemate}{$ \node $}
            \State $ \node(x,y) \gets \nodePrevious(x,y) $

@@

            \ForEach{$ \nodeInCorridorEach $ inside $ corridor $}

                \State $ \Vector{\nodeInCorridorEach ~\nodeInCorridorEach.next} = \nodeVectorPC $

                \State $ \nodeInCorridorEach(x,y) \gets \nodeInCorridorEach.next(x,y) $

@@

    \textbf{Input:} \\
    $ \Edge \gets $ the edge used to derive the parallel edge $ \EdgeParallel $ \\
    $ \Distance \gets $ the shortest distance between $ \Edge $ and $ \EdgeParallel $ \\
